A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-12 12_conclusions_future_work.tex
Tim: spell check

\begin{itemize}
\item Accurate filling using few/small overfill and underfill areas
\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
\item Our framework is able to emulate several methods proposed in related literature.
\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
\item Our framework is stable against slight perturbations of the outline shape or large perturbations of the outline shape in far away regions.
\item We can define a strategy which distibutes the bead width deviation over a small region so as to retain smooth toolpaths of nominal width throughout the larger part of big regions.
\item Our strategy keep mechanical properties more constant.
\item The computation times are approximately 3(?) times as fast as the state of the art method for naive toolpath generation employing constant width.
\end{itemize}

>>>>

\begin{itemize}
\item Accurate filling using few/small overfill and underfill areas
\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
\item Our framework is able to emulate several methods proposed in related literature.
\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
\item Our framework is stable against slight perturbations of the outline shape or large perturbations of the outline shape in far away regions.
\item We can define a strategy which distributes the bead width deviation over a small region so as to retain smooth toolpaths of nominal width throughout the larger part of big regions.
\item Our strategy keep mechanical properties more constant.
\item The computation times are approximately 3(?) times as fast as the state of the art method for naive toolpath generation employing constant width.
\end{itemize}

### 2019-08-12 4_method.tex
Tim: spell check

\section{Method}
When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
We decide on a bead count at locations which lie in centeral positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the centeral regions outward.

@@

Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is disctoninuous,
or it can be defined as the locations where wavefront propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wavefronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

\begin{figure}
\centering
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
\caption{Circles}
\label{MAT_explanation_circles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
\caption{Wavefronts}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
\caption{Cones}
\end{subfigure}
\caption{
Medial axis representations.
The medial axis can be defined in terms of the the number of support points of the inscribed circles,
as the pinch sites in wavefronts
or as ridges in a volume defined by the union of cones.
}
\label{MAT_explanation}
\end{figure}

@@

\subsubsection{Skeletal trapezoidation}
We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
We repesent such a skeleton in a standard half-edge datastructure.
See \cref{shape_decomposition_simple}.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and \cref{shape_decomp_complex}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical represenatation of the medial axis; see \cref{mat_3d}.

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which arew in some sense \emph{central} to the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a naive beading using a constant bead witdh $w$ of a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

@@

\subsubsection{Transitioning}
In order to prevent discontinuities in the toolpaths around locations where the bead count changes, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
See \cref{transitions}.
The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
Because transitions in bead count only occurs in locations where the prefered bead count $b$ changes, we introduce $b^{-1}(n) := \argmax_d b(d) = n$.

@@

In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the coresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
See \cref{beading_transitioning_filtering__transition_ends}.
These fractional bead counts will be used in \cref{section_beading_interpolation}.

@@

The following restrictions hold:
\begin{itemize}
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Skeletal nodes which are in the middle of a transition have obtained a fractional bead count, but the functions defined in the beading strategy are only defined on natural numbers.
The fractional part of the bead count is used to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \frac12 n^{B^V}$ linearly and enforce the symmetry contraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the skeleton inside of transition regions.

@@

We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
See \cref{segment_generation}.
If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
If a central edge has both nodes with an odd beadcount assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center segment from both trapezoids.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.

Each of the trapezoids is connceting to a single outline polygon.
By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.
See \cref{segment_generation}.
In a final step we connect the ends of polylines together, so that the final toolpaths contain both polygons and polylines.

>>>>

\section{Method}
When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
We decide on a bead count at locations which lie in central positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the central regions outward.

@@

Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is discontinuous,
or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

\begin{figure}
\centering
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
\caption{Circles}
\label{MAT_explanation_circles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
\caption{Wave-fronts}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
\caption{Cones}
\end{subfigure}
\caption{
Medial axis representations.
The medial axis can be defined in terms of the the number of support points of the inscribed circles,
as the pinch sites in wave-fronts
or as ridges in a volume defined by the union of cones.
}
\label{MAT_explanation}
\end{figure}

@@

\subsubsection{Skeletal trapezoidation}
We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
We represent such a skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_simple}.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and \cref{shape_decomp_complex}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical representation of the medial axis; see \cref{mat_3d}.

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which are in some sense \emph{central} to the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a naive beading using a constant bead width $w$ of a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

@@

\subsubsection{Transitioning}
In order to prevent discontinuities in the toolpaths around locations where the bead count changes, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
See \cref{transitions}.
The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
Because transitions in bead count only occurs in locations where the preferred bead count $b$ changes, we introduce $b^{-1}(n) := \argmax_d b(d) = n$.

@@

In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
See \cref{beading_transitioning_filtering__transition_ends}.
These fractional bead counts will be used in \cref{section_beading_interpolation}.

@@

The following restrictions hold:
\begin{itemize}
\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}

@@

\subsubsection{Beading interpolation}\label{section_beading_interpolation}
Skeletal nodes which are in the middle of a transition have obtained a fractional bead count, but the functions defined in the beading strategy are only defined on natural numbers.
The fractional part of the bead count is used to interpolate between two beadings defined on the fractional bead count rounded up and down.
Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \frac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
See \cref{beading_interpolation}.
The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the skeleton inside of transition regions.

@@

We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
See \cref{segment_generation}.
If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center segment from both trapezoids.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.

Each of the trapezoids is connecting to a single outline polygon.
By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.
See \cref{segment_generation}.
In a final step we connect the ends of polylines together, so that the final toolpaths contain both polygons and polylines.

### 2019-08-12 6_validation.tex
Tim: spell check

We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
$$t_0(n) =  t(n) \left( b^{-1}(n) / 0.4  - n \right)$$
This should ensure that the transitions never overlap with the locations $v$ where $2 R(v) = 0.4n$ for $n \in \mathbb{N}$, since \SI{0.4}{\milli\meter} is the prefered bead width for a similar nozzle size.

Our beading strategies are based on a prefered width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.

@@

\paragraph{Distributed strategy}
Distribute the overfill or underfill which would happen using a naive strategy over all beads.
This maximizes robustness and minimizes narrow beads qhich are difficult to print.

@@

\paragraph{Inward distributed strategy}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
To distribute the hypothetical over-/underfill over the innermost $2N$ beads, and distribute most of it to the inner beads.
That way we limit the impact of the distributed strategy and have the nominal bead width $w_\text{pref}$ in regions farther away from the middle.
This helps if print settings for bead widths other than the prefered width aren't calibrated as well as the settings for $w_\text{pref}$.
Toolpaths with deviating widths might result in less dimensional accuracy on the outline and uncalibrated mechanical properties throughout the volume, so limiting the number of beads width deviating bead width might be beneficial.
\todo{Emphasize this point more. Put it in the abstract and conclusion.}

@@

We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then takign the difference from the original outline shape.
In order to deal with rounding errors we perform a morpholocial close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
These tripple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualzied for the different toolpath strategies in the top of \cref{visualized_accuracy}.

>>>>

We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
$$t_0(n) =  t(n) \left( b^{-1}(n) / 0.4  - n \right)$$
This should ensure that the transitions never overlap with the locations $v$ where $2 R(v) = 0.4n$ for $n \in \mathbb{N}$, since \SI{0.4}{\milli\meter} is the preferred bead width for a similar nozzle size.

Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.

@@

\paragraph{Distributed strategy}
Distribute the overfill or underfill which would happen using a naive strategy over all beads.
This maximizes robustness and minimizes narrow beads which are difficult to print.

@@

\paragraph{Inward distributed strategy}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
To distribute the hypothetical over-/underfill over the innermost $2N$ beads, and distribute most of it to the inner beads.
That way we limit the impact of the distributed strategy and have the nominal bead width $w_\text{pref}$ in regions farther away from the middle.
This helps if print settings for bead widths other than the preferred width aren't calibrated as well as the settings for $w_\text{pref}$.
Toolpaths with deviating widths might result in less dimensional accuracy on the outline and uncalibrated mechanical properties throughout the volume, so limiting the number of beads width deviating bead width might be beneficial.
\todo{Emphasize this point more. Put it in the abstract and conclusion.}

@@

We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
In order to deal with rounding errors we perform a morpholocical close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
These triple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
